\Large {\bf rt1d: Documentation}

### 2012-05-01 doc/manual/rt1d_manual.tex
Hubble cooling working - must be careful with decoupling redshift - need to work on Compton scattering in order for this to be solved self-consistently.

>>>>

% Cosmology
\subsection{Additional Complexity: Cosmological Expansion}
For an expanding universe, things are slightly more complicated, as ion densities will have an additional term $\propto (1 + z)^3$, and we must take into account Hubble cooling, and Compton scattering of CMB photons.

We must also modify the minimum and maximum column densities for our integral tables.  To calculate what these should be for a simulation spanning the redshift interval $(z_i, z_f)$, minimum species fraction $x_{\mathrm{min}}$, and grid resolution (in proper coordinates) $dx$, do
\begin{align}
    N_{\HI}^{\mathrm{min}} & = \bar{n}_H^0 (1 + z_f)^3 dx x_{\mathrm{min}}   \\
    N_{\HI}^{\mathrm{max}} & = \bar{n}_H^0 (1 + z_i)^3 \Lbox .
\end{align}
